% PyBaMM Conference 2026 --- 1-page abstract, V5 (theta-conditioned neural operator)
% Author: Krishna Chaitanya Vaddepally, Turno (Blubble Pvt. Ltd.)
% Deadline: 2026-07-15 UTC
%
% V5 (revised): rewritten in the Book of Abstracts style --- three flowing
% paragraphs, no equations, no implementation minutiae. Central result
% updated to the end-to-end validation from a single characterised cell.
% Layout matches the accepted talk abstracts on pp. 6, 17, 19, 24 of the
% PyBaMM Conf. 2025 Book of Abstracts: bold centred title, single author
% block, three flowing paragraphs, numbered references at the foot.
\documentclass[12pt,a4paper]{article}

\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

\usepackage[a4paper,top=1.8cm,bottom=1.8cm,left=1.8cm,right=1.8cm]{geometry}
\usepackage{graphicx}
\usepackage{caption}
\usepackage{microtype}
\usepackage{xcolor}
\usepackage[hidelinks]{hyperref}
\usepackage{setspace}
\usepackage{enumitem}
\setstretch{1.05}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0.45em}

\pagestyle{empty}

\begin{document}

\begin{center}
{\large\textbf{From a single characterisation snapshot to end-of-life:\\
a PyBaMM-trained neural operator for second-life LFP RUL}}\\[0.55em]
\underline{Krishna Chaitanya Vaddepally}\\
\emph{Turno (Blubble Pvt.\ Ltd.), Bengaluru, India}\\
\texttt{krishna.vaddepally@turno.club}
\end{center}

\vspace{0.15em}

Second-life reuse of used lithium-iron-phosphate (LFP) cells for
stationary energy storage is bottlenecked by characterisation cost.
Per-cell PyBaMM~[1] calibration of degradation parameters against
measured state-of-health (SoH) trajectories requires at least 400
cycles per cell~[2] to reliably extrapolate to end-of-life; below
that, the fitted rates become under-determined. Prior second-life
work~[3] and universal-differential-equation degradation~[4] improve
the quality of the per-cell fit but do not shrink the cycling budget
itself. Reducing that budget requires transferring knowledge from a
synthetic parameter-space corpus to individual cells rather than
fitting each from scratch.

The approach has two stages. A corpus of 300 synthetic degradation
trajectories is first generated with PyBaMM's DFN model using the
Prada2013~[2] LFP chemistry and per-cell beginning-of-life parameters
identified from OCV, GITT, HPPC and RPT tests on a fresh supplier-B
cohort. A Sobol sweep across five degradation channels --- SEI
kinetics, plating current, positive- and negative-electrode
active-material loss, and SEI molar volume --- spans the
physically-plausible parameter space at 25\,\textdegree C, producing
300 trajectories paired with the degradation-parameter vector
$\theta$ that generated each. A DeepONet~[5] variant is then trained
to map a five-stream fingerprint (DCIR, RPT features, the first-$K$
measured SoH values, $\theta$, and cycling protocol) onto the SoH
trajectory at any queried cycle. Conditioning on $\theta$ lets the
operator absorb electrochemistry directly from the identification
step rather than reconstructing it from characterisation alone.

End-to-end validation on a single supplier-B cell drives both the BOL
identification and the degradation-parameter fit from that cell's own
data. Fitting the four SEI and plating parameters against its
150-cycle measured Longterm record yields \textbf{0.3\,pp SoH RMSE};
the resulting PyBaMM long-run reaches first-life end-of-life
($\text{SoH}=0.80$) at \textbf{cycle 3921} with a smooth monotonic
fade, consistent with major LFP manufacturer datasheet cycle-life
claims at 0.5\,C. In this presentation the trained operator's
predictions on 20 held-out cells across three commercial LFP
suppliers will be shown, together with the identifiability limits of
parameter fitting from short cycling records and extensions to
non-isothermal deployment.

\vspace{0.4em}
{\footnotesize
\textbf{References}
\begin{enumerate}[leftmargin=1.6em,itemsep=-0.15em,topsep=0.15em,labelsep=0.4em]
\item V. Sulzer \emph{et al.}, PyBaMM, \emph{J. Open Res. Softw.}\ \textbf{9}(1), 14--21 (2021).
\item M. Prada \emph{et al.}, Simplified electrochemical and thermal model of LiFePO$_4$-graphite Li-ion batteries, \emph{J. Electrochem. Soc.}\ \textbf{160}(4), A616--A628 (2013).
\item O. Ouledboutaarija \emph{et al.}, Advancing Second-Life Lithium-Ion Batteries, PyBaMM Conf.\ 2025, p.\ 19.
\item J. A. Kuzhiyil \emph{et al.}, Enhancing Generalisability of Physics-based Battery Degradation Using UDE, PyBaMM Conf.\ 2025, p.\ 12.
\item L. Lu \emph{et al.}, DeepONet: learning nonlinear operators for identifying differential equations, \emph{Nat. Mach. Intell.}\ \textbf{3}, 218--229 (2021).
\end{enumerate}
\par}

\end{document}
